The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-25 article.tex

   To evaluate the performance of the CDK molecular formula generator, we
compared its runtimes to those of the classic, full enumeration-based HR2
formula generator~\cite{Kind2007} and those of a recently developed Parallel
Formula Generator (PFG)~\cite{Zhang2016} (Table~1\ref{tab:formula_generators}).
As inputs, we used two sets of $10\,000$ small ($< 500$~Da) and $20$ large ($>
1\,500$ and $< 3\,500$~Da) molecular mass values downloaded from the Global
Natural Products Social Molecular Networking database~\cite{wang2016}. The mass
tolerance was set to 0.001 or 0.01 Da. The CDK's Round-Robin formula generator
outperformed the other methods in all cases, despite running in a single thread
(PFG utilizes multiple threads).

>>>>

   To evaluate the performance of the CDK molecular formula generator, we
compared its runtimes to those of the classic, full enumeration-based HR2
formula generator~\cite{Kind2007} and those of a recently developed Parallel
Formula Generator (PFG)~\cite{Zhang2016} (Table~1\ref{tab:formula_generators}).
As inputs, we used two sets of $10\,000$ small ($< 500$~Da) and $20$ large ($>
1\,500$ and $< 3\,500$~Da) molecular mass values downloaded from the Global
Natural Products Social Molecular Networking database~\cite{wang2016}. The mass
tolerance was set to 0.001 or 0.01 Da. The CDK \cdkversion{}'s Round-Robin 
formula generator outperformed the other methods in all cases, despite running
in a single thread (PFG utilizes multiple threads). The performance gain of
the Round Robin algorithm was particularly apparent when narrow mass ranges 
were queried (e.g., $\pm 0.001$ Da), thus showing its suitability for
applications in high-resolution mass spectrometry.
